\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-07-29 ndss/main.tex
added ndss version.

\documentclass[sigconf, anonymous]{acmart}

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Anonymous submission \#410 to ACM CCS 2017} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
\acmYear{2017}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained

\input{headers}

@@

@@

\setlength\intextsep{1pt}
\setlength{\textfloatsep}{1pt}
\setlength{\abovecaptionskip}{4pt}
\setlength{\belowcaptionskip}{4pt}

@@

{\footnotesize \bibliographystyle{acm}
\bibliography{bib}}

>>>>

\documentclass[conference]{IEEEtran}

\pagestyle{plain}
\input{headers}

@@

%\setlength\intextsep{1pt}
%\setlength{\textfloatsep}{1pt}
%\setlength{\abovecaptionskip}{4pt}
%\setlength{\belowcaptionskip}{4pt}

@@

@@

\bibliographystyle{IEEEtranS}
\bibliography{bib}
